%%%% ijcai17.tex

\typeout{IJCAI-17 Instructions for Authors}

% These are the instructions for authors for IJCAI-17.
% They are the same as the ones for IJCAI-11 with superficical wording
%   changes only.

\documentclass{article}
% The file ijcai17.sty is the style file for IJCAI-17 (same as ijcai07.sty).
\usepackage{ijcai17}

% Use the postscript times font!
\usepackage{times}

\usepackage{amssymb}
\usepackage{tikz}
%\usetikzlibrary{bayesnet}
\usepackage{diagbox}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{amsthm}       %% The amsthm package provides extended theorem environments
\usepackage{multirow}
\usepackage{algorithmic}
\newcommand{\dir}{\text{Dir}}
\newcommand{\mult}{\text{Multi}}
\newtheorem{example}{Example}
\usepackage{amstext}
\usepackage{hyperref}
\newtheorem{definition}{Definition}
%\newcommand{\upcite}[1]{\textsuperscript{\textsuperscript{\cite{#1}}}}
%\usepackage{algorithm}
%\usepackage{algorithmic}
\makeatletter
\newif\if@restonecol
\makeatother
\let\algorithm\relax
\let\endalgorithm\relax
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{enumerate}

% the following package is optional:
%\usepackage{latexsym}

% Following comment is from ijcai97-submit.tex:
% The preparation of these files was supported by Schlumberger Palo Alto
% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
% preparation.

% These instructions can be modified and used in other conferences as long
% as credit to the authors and supporting agencies is retained, this notice
% is not changed, and further modification or reuse is not restricted.
% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
% contacts for providing assistance without their prior permission.

% To use for other conferences, change references to files and the
% conference appropriate and use other authors, contacts, publishers, and
% organizations.
% Also change the deadline and address for returning papers and the length and
% page charge instructions.
% Put where the files are available in the appropriate places.

\title{Knowledge Graph Embedding With Attentional Triple Context}
\author{Huan Gao$^{1,2}$, Jun Shi$^{1,2}$, Guilin Qi$^{3}$\\
$^{1}$School of Computer Science and Engineering,
Southeast University, Nanjing, China  \\
%qiuji@njupt.edu.cn\\
}

\begin{document}

\maketitle

\begin{abstract}
    Knowledge graph embedding can represents entities and relations with efficient low-dimensional embedding vectors. The outstanding performance on knowledge graph completion has led to an increase in the knowledge graph embedding research. State-of-the-art knowledge graph embedding approaches treat each triple independent and neglect structure information. However, as a fact, the rich graph features in knowledge graph can be considered as contexts of a triple which contain large information to describe entities and relations. In this paper, we proposes an Attentional-Triple-Context-based knowledge Embedding model(ATCE), which formulates a local structures around a triple as a context. For each triple, two kinds of structure information are considered as its context, which we refer to \emph{as triple context} : 1) Neighbor context is the outgoing relations and neighboring entities of an entity; 2) Path context is connective relation paths between a pair of entities, both of which contains rich useful and unrelated information for entities and relations. ATCE learns embedding for entities and relations with a attention mechanism and is expected to select the useful information in triple context. The experimental results show that our model outperforms the state-of-the-art methods for link prediction and entity prediction.
\end{abstract}



\input{intro}
\input{trp}
\input{model}
\input{exp}
\input{rel}
\input{conc}


%% The file named.bst is a bibliography style file for BibTeX 0.99c
\bibliographystyle{named}
%\bibliographystyle{unsrt}
\bibliography{bibOfTex}

\end{document}

